Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-01 draft.tex
small stuff

@@

@@

>>>>

\owen{I want to recall briefly how an $L_\infty$ action on a cochain complex leads to all the variants of CE (co)chains.}

@@

\begin{lmm}
\label{lmm: CE from map}
\owen{an $L_\infty$ map $\fg \rightsquigarrow \fh$ induces a cochain complex $\clies(\fg,\cliels(\fh))$.}
\end{lmm}

@@

Our goal here is to construct the factorization algebra that models the centralizer.
First, we need to show that there is a well-defined functor (in the 1-categorical sense) ${\rm Opens}_{\RR^n} \to \Ch_k$ assigning $\clies(\Omega^*(V) \otimes \fg, \bU_n \fh(V))$ to each open set $V$.
Once that is in place, it is straightforward to describe the structure maps of the prefactorization algebra.

The role of
